---
title: "test_final_project"
author: " 1"
date: "4/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




```{r}
library(tidyverse)
data <- read_csv("Mixed_data.csv")
colnames(data)[1]<-"region"
data[[1]]<-tolower(data[[1]])
#data<-data[-c(52),]
data$Offenses<-as.numeric(data$Offenses)
data$Population<-as.numeric(data$Population)
data$`Median Income`<-as.numeric(data$`Median Income`)
data$`Citizenship Status`<-as.numeric(data$`Citizenship Status`)
data$`Unemployment Rate`<-as.numeric(data$`Unemployment Rate`)
data$`Education Level`<-as.numeric(data$`Education Level`)
data$`Race/Ethnicity`<-as.numeric(data$`Race/Ethnicity`)
colnames(data)[7]<-"Political_party"
data$crime_rate<-data$Offenses/data$Population*100
```
```{r}
library(gdata)
library(readxl)
library(ggplot2)
library(ggpubr)
library(wordcloud2)
library(treemap)
class<-read_excel("table-1.xls",sheet=1,na="NA")
total_distribution = class[c(6,16,31,37,40,43),c(1,2)]
colnames(total_distribution)[1]<-"Class"
colnames(total_distribution)[2]<-"freq"
total_distribution$freq<-as.numeric(total_distribution$freq)
total_distribution$fraction = total_distribution$freq / sum(total_distribution$freq)
total_distribution$ymax = cumsum(total_distribution$fraction)
total_distribution$ymin = c(0, head(total_distribution$ymax, n=-1))
#ggdonutchart(total_distribution,"Class",fill="freq",color="white")
ggplot(data = total_distribution, mapping = aes(x = 1, y = freq, fill = Class)) + geom_bar(stat = 'identity', position = 'stack', width =0.2)+
coord_polar(theta = 'y')


ggplot(total_distribution,aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=Class)) +
     geom_rect() +
     coord_polar(theta="y") + # Try to remove that to understand how the chart is built initially
     xlim(c(2, 4))+theme_void()+
    #geom_text(aes(x = 4.6, y = ((ymin+ymax)/2),label = freq) ,size=4)+
  geom_text(aes(x = 3.5, y = ((ymin+ymax)/2),label = Class) ,size=3.6)# Try to remove that to see how to make a pie chart
 #wordcloud2(total_distribution, size = 1,shape = 'star')
small_class<-class[-c(1,2,3,4,5,6,16,31,37,40,43,46,47,48,49),c(1,2,6)]
colnames(small_class)[1]<-"Class"
colnames(small_class)[2]<-"freq"
colnames(small_class)[3]<-"category"
small_class$freq<-as.numeric(small_class$freq)
wordcloud2(small_class, size = 2,color = "random-light", shape = 'diamond',backgroundColor = "white")

#wordcloud2(demoFreq, size=0.5,shape="star")
treemap(small_class,index = c("category","Class"), vSize = "freq", vColor = "Class",type="index",title='Treemap of Bias motivation in hate crime in US', palette = "RdBu")
```
The graph above shows the distribution of bias motivation in 2019.  We can see that the motivations for hate are as diverse as the people who form the racial, religious, and mixed-gender melting pot that is the United States of America. There are six main types of bias motivation including Race/Ethnicity/Ancestry/Bias, Religion, Sexual Orientation, Gender Identity, Disability and Gender, of which the largest proportion is Race/Ethnicity/Ancestry Bias, accounting for more than 50% of all. It means bias between different races is the main cause of most hate crimes. In addition, different religious beliefs may also lead to some hate crimes, which may be due to the exclusivity of some religious beliefs to some extend. The bias motivation of hate crime are not only towards some specific minorities, it exists anywhere between many different groups.










```{r,fig.width=10 fig.height=12}
library(tidyverse)
library(choroplethr)
df_illiteracy <- state.x77 %>% as.data.frame() %>% 
  rownames_to_column("state") %>% 
  transmute(region = tolower(`state`), value = Illiteracy)
x2<-state.x77
#state_choropleth(df_illiteracy,title = "State Illiteracy Rates, 1977",legend = "Percent Illiterate")
offense_state <- data[-c(52),c(1,10)]
#offense_state$Offenses<-as.numeric(offense_state$Offenses)
colnames(offense_state)[2]<-"value"
#offense_state[is.na(offense_state)] <- 0
state_choropleth(offense_state,title = "State Crime, 2019",num_colors = 6,legend = "count")
education_state<-data[-c(52),c(1,4)]
education_state$`Education Level`<-as.numeric(education_state$`Education Level`)
colnames(education_state)[2]<-"value"
state_choropleth(education_state,title = "State Education Level",num_colors = 6,legend = "scores")

plot(x=education_state$value, y=offense_state$value, main = "Education Level - Hate Crime Rate")

ed_hate_crime<-data[-c(9,52),]
ggplot(ed_hate_crime,aes(`Education Level`, crime_rate,colour = `Political_party`))+geom_point()+labs(x="Education Level",y="Hate Crime Rate")+scale_x_continuous(breaks=seq(0,100,10))
ggplot(ed_hate_crime,aes(`Unemployment Rate`, crime_rate,colour = `Political_party`))+geom_point()+labs(x="Unemployment",y="Hate Crime Rate")+scale_x_continuous(breaks=seq(0,100,10))
ggplot(ed_hate_crime,aes(`Median Income`, crime_rate,colour = `Political_party`))+geom_point()+labs(x="Median Income",y="Hate Crime Rate")+scale_x_continuous(breaks=seq(0,100,10))
ggplot(ed_hate_crime,aes(`Race/Ethnicity`, crime_rate,colour = `Political_party`))+geom_point()+labs(x="Race/Ethnicity",y="Hate Crime Rate")+scale_x_continuous(breaks=seq(0,100,10))

ggplot(ed_hate_crime,aes(Population, Offenses,colour = `Political_party`))+geom_point()+labs(x="Population",y="Hate Crime")+scale_x_continuous()


```










```{r,fig.width=10, fig.height=12}
library(ggplot2)
library(GGally)
data_new<-data[-c(52),]
ggpairs(data_new,column = c(2,3,4),cardinality_threshold = 51)
```




```{r, echo=TRUE}
library(devtools)
library(ggplot2)
library(EDAWR)
library(GGally)
library(dplyr)

ggparcoord(data,columns = c(10,3,4,5,6) ,groupColumn = 'region', alphaLines = 0.8, splineFactor = 10,order = "skewness") +
  xlab("Columns")+
  theme(legend.position = "none")
ggparcoord(data,columns = c(1,7) , alphaLines = 0.8) +
  xlab("Columns")+
  theme(legend.position = "none")

```